%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education \& Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Radboud University Medical Center} % Institution
    {PhD Deep Learning for Medical Imaging} % Degree
    {Nijmegen, The Netherlands} % Location
    {Oct. 2019 - Oct. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Development and evaluation of deep learning models for adhesion detection on cine-MRI}
        \item {Generative medical imaging with latent diffusion models}
        \item {Uncertainty quantification for medical imaging}
      \end{cvitems}
    }

  \cventry
    {University of Twente} % Institution
    {MSc Applied Physics + Applied Mathematics} % Degree
    {Enschede, The Netherlands} % Location
    {Sep. 2016 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Specialization Materials Science and Scientific Computing + Research Honours Track}
        \item {Numerical simulation of hopping transport in disordered dopant networks}
      \end{cvitems}
    }

  \cventry
    {Cloud and Computing Infrastructure Department} % Institution
    {Internship IBM Research} % Degree
    {Zurich, Zwitserland} % Location
    {Sep. 2017 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Experiments and simulations on 1/f noise in phase-change memory devices}
      \end{cvitems}
    }

  \cventry
    {University of Twente} % Institution
    {BSc Applied Physics} % Degree
    {Enschede, The Netherlands} % Location
    {Sep. 2013 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Minor in secondary school Physics education}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
